### 2015-10-15 rscripts/location_clusters.Rmd
update tests
working covert sim

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="user categorization, by primary location type utilization"}
plot_ref <- ref[
  lifetime_dts$digest[, list(lifetime_main = main, lifetime_share = share), keyby=user_id]
][
  pwr_dts$digest[, list(pwr_main = main, pwr_share = share), keyby=user_id]
][
  vMF_dts$digest[, list(peak_main = main, peak_share = share), keyby=user_id]
]
user_src.dt <- plot_ref[between(life, 365*24*60*60, 3*365*24*60*60) & between(ul,3,20)]
#thing[, list(user_id, mains=interaction(lifetime_main, pwr_main, peak_main))][,.N,by=mains]
ggplot(user_src.dt[, list(y=log10(usage), x=log10(life), pwr_main, lifetime_main, peak_main, membership = lifetime_share * pwr_share * peak_share)]) +facet_grid(pwr_main ~ lifetime_main, labeller = function(var, val){
  if (var == "pwr_main") {
    ifelse(val == "lo", "smooth usage", ifelse(val=="med","some usage variability","highly variable usage"))
  } else {
    ifelse(val == "low", "low usage per time", ifelse(val=="mid","typical usage per time","high usage per time"))
  }
}) + aes(x=x,y=y, color=factor(peak_main), alpha = membership) + geom_point() + theme_bw() + labs(y="log(usage)", x="log(life)", color="usage\npeak")
```
\elandscape\newpage

```{r, echo=F}
# thing <- 
#   data.table(
#     x=lifetime_dts$digest[, list(pos = (0.5*`2`+1*`3`)/(`1`+`2`+`3`), main, share, user_id)]$pos,
#     y=pwr_dts$digest[, list(pos = (0.5*`2`+1*`3`)/(`1`+`2`+`3`), main, share, user_id)]$pos,
#     z=vMF_dts$digest[, list(pos = (0.5*`2`+1*`3`)/(`1`+`2`+`3`), main, share, user_id)]$pos,
#     key=c("x","y","z")
#   )
# uthing <- unique(thing)
# lenthing <- dim(uthing)[1]
# cloud(z ~ x*y, data=unique(thing)[sample.int(lenthing, 250)])
# censor.dt[user_id %in% user_src.dt$user_id, .N*60*60*24*30/(max(logout)-min(login)), by=user_id][V1>1]
```

>>>>

\newpage\blandscape
```{r, echo=F, fig.width=11.25, fig.height=7, fig.cap="user categorization, by primary location type utilization"}
plot_ref <- ref[
  lifetime_dts$digest[, list(lifetime_main = main, lifetime_share = share), keyby=user_id]
][
  pwr_dts$digest[, list(pwr_main = main, pwr_share = share), keyby=user_id]
][
  vMF_dts$digest[, list(peak_main = main, peak_share = share), keyby=user_id]
]
user_src.dt <- plot_ref[between(life, 365*24*60*60, 3*365*24*60*60) & between(ul,3,20)]
saveRDS(user_src.dt, "../input/user.RData")
#thing[, list(user_id, mains=interaction(lifetime_main, pwr_main, peak_main))][,.N,by=mains]
ggplot(user_src.dt[, list(y=log10(usage), x=log10(life), pwr_main, lifetime_main, peak_main, membership = lifetime_share * pwr_share * peak_share)]) +facet_grid(pwr_main ~ lifetime_main, labeller = function(var, val){
  if (var == "pwr_main") {
    ifelse(val == "lo", "smooth usage", ifelse(val=="med","some usage variability","highly variable usage"))
  } else {
    ifelse(val == "low", "low usage per time", ifelse(val=="mid","typical usage per time","high usage per time"))
  }
}) + aes(x=x,y=y, color=factor(peak_main), alpha = membership) + geom_point() + theme_bw() + labs(y="log(usage)", x="log(life)", color="usage\npeak")
```
\elandscape\newpage

```{r, echo=F}
saveRDS(agg.dt[,list(lifetime_cat, pwr_clust, vMFcluster), by=location_id], "../input/locClusters.RData")
intermediate <- censor.dt[user_id %in% user_src.dt$user_id, list(visits = .N), by=list(user_id, location_id)][,
  list(location_id, pref=visits/sum(visits)), keyby=user_id
][,list(user_id, pref), keyby=location_id]
saveRDS(intermediate[agg.dt[location_id %in% unique(intermediate$location_id), list(lifetime_cat, pwr_clust, vMFcluster), keyby=location_id]][,
  list(lifetime_cat, pwr_clust, vMFcluster, pref),
  keyby=user_id
],"../input/userPrefs.RData")

#[,.N,keyby=list(user_id, lifetime_cat, pwr_clust, vMFcluster)][,list(pref = N/sum(N),keyby=list(user_id, lifetime_cat, pwr_clust, vMFcluster)]
# thing <- 
#   data.table(
#     x=lifetime_dts$digest[, list(pos = (0.5*`2`+1*`3`)/(`1`+`2`+`3`), main, share, user_id)]$pos,
#     y=pwr_dts$digest[, list(pos = (0.5*`2`+1*`3`)/(`1`+`2`+`3`), main, share, user_id)]$pos,
#     z=vMF_dts$digest[, list(pos = (0.5*`2`+1*`3`)/(`1`+`2`+`3`), main, share, user_id)]$pos,
#     key=c("x","y","z")
#   )
# uthing <- unique(thing)
# lenthing <- dim(uthing)[1]
# cloud(z ~ x*y, data=unique(thing)[sample.int(lenthing, 250)])
# censor.dt[user_id %in% user_src.dt$user_id, .N*60*60*24*30/(max(logout)-min(login)), by=user_id][V1>1]
```

show swtiching rate normalized by visit rate on a per user basis

show 27 categories
